Transient dynamics of granular piles: continuum v discrete modelling

### 2016-07-13 paper.tex
Added abstract

\begin{abstract}
%% Text of abstract
Click here and insert your abstract text.
\end{abstract}

>>>>

\begin{abstract}
Transient granular flows, such as rock falls, debris flows, and aerial and submarine avalanches, occur very often in nature. In the geotechnical context, transient movements of large granular slopes are a substantial factor of risk due to their destructive force and the transformations they may produce in the landscape. This paper investigates the ability of MPM, a continuum approach, to reproduce the evolution of a granular pile destabilised by an external energy source. In particular, a central issue is whether the power-law dependence of run-out distance and time observed with respect to the initial geometry or energy can be reproduced by a simple Mohr-Coulomb plastic behaviour for granular slopes subjected a horizontal excitation. The effects of different input parameters, such as the distribution of energy and base friction, on the run-out kinematics are studied by comparing the data obtained from DEM and MPM simulations. The mechanism of energy dissipation is primarily through friction and MPM is able to predict the run-out response in good agreement with DEM simulations. At very low energy, DEM simulations show longer run-out in the case of slope subjected to excitations due to local destabilization at the flow front. At low input energy, the gradient velocity distribution shows significantly longer run-out in comparison to uniform velocity distribution. At low input energies a larger fraction of the energy is consumed in the destabilisation process, hence the amount energy available for flow is less in uniform velocity distribution than the gradient velocity profile. However, at higher input energy, where most of the energy is dissipated during the spreading phase, the run-out distance has a weak dependence on the distribution of velocity in the granular mass.
\end{abstract}
